---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dqtesting

The goal of the package is to provide an easy toolset for data quality testing. The main function `perform_dqtest` returns a list containing various results from an univariate DQ test. Moreover functions are provided that allow a very easy interface to the Local Outlier Factor Algorithm for multivariate outlier detection (therefore automated hyperparameter tuning). 

## Web Interface

There is a web application to the package: [Link](https://esommer.shinyapps.io/dqtesting/)

## Installation

You can install the released version of dqtesting from Github in R with the following line of code:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EmanuelSommer/dqtesting")
```

## Some examples

The `dummy_data` is a dummy data set contained in the package.

```{r data}
library(dqtesting)
# quick overview of the dummy data
str(dummy_data)
```

These are basic examples which show you how to solve some common problems:

Given: The data should not contain missing values, the data should have a certain range or contain categories and moreover some values can be excluded as they represent special cases. To check these data quality requirements the function `perform_dqtest` can be used in the following way. 

```{r example}
library(dqtesting)
### first variable: char1 with allowed categories "Random Forest", "Linear Regression" and "SVM", "Neural Networks" should be excluded.
dq_char <- perform_dqtest(dummy_data$char1,
                          categories = c("Random Forest","Linear Regression","SVM"),
                          exclude_values = "Neural Networks")
# access the absolute and relative amount of NA's
dq_char$abs_na
dq_char$rel_na

# access the absolute and relative amount of excluded values
dq_char$exclusions$abs_excluded
dq_char$exclusions$rel_excluded

# access a statistical summary
dq_char$stat_summary

# access the categories check
dq_char$cat_check

# access a visualisation
dq_char$barplot

### second variable: num2 should be non negative
dq_num <- perform_dqtest(dummy_data$num2, range_min = 0)

# access the 0.4 quantile of the vector
dq_num$stat_summary$quantiles11[4]

# access the minimum of the vector
dq_num$stat_summary$quantiles11[1]

# access the range check
dq_num$range_check

# access a different visualisation
dq_num$boxplot

### third variable: datetime2
dq_datetime <- perform_dqtest(dummy_data$datetime2)

# access a visualisation about the weekdays
dq_datetime$hist_wday
```

These were just a few examples of this very flexible function. 

If multivariate outliers should be detected too, the package provides some useful functions:

```{r example2}
# perform the LOF Algorithm
lof_list <- lof_fun(dummy_data[,c(3,4)])
# extract the most suspicious values
extract_rows_score(dummy_data[,c(3,4)],lof_list,threshold = 1.5)
# visualize the results
lof_vis(dummy_data[,c(3,4)],lof_list)
```

Detailed help pages are available for all functions. For example just type `?perform_dqtest` into the console.

Have fun :)


